Squintability and Other Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimization Choices

### 2025-11-22 jso.tex
knit the pdf

\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, coltitle=black, opacitybacktitle=0.6, title={Algorithm: Jellyfish Optimizer Pseudo Code}, breakable, opacityback=0, toprule=.15mm, left=2mm, bottomtitle=1mm, rightrule=.15mm, bottomrule=.15mm, titlerule=0mm, colframe=quarto-callout-note-color-frame, colback=white, leftrule=.75mm, toptitle=1mm]

>>>>

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colback=white, title={Algorithm: Jellyfish Optimizer Pseudo Code}, colframe=quarto-callout-note-color-frame, toprule=.15mm, arc=.35mm, opacityback=0, opacitybacktitle=0.6, bottomrule=.15mm, breakable, left=2mm, coltitle=black, bottomtitle=1mm, toptitle=1mm, colbacktitle=quarto-callout-note-color!10!white, leftrule=.75mm, titlerule=0mm]
